{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added categories of side channels

>>>>

The idea is to 'track and regulate' \cite{Zdancewic04} where information flows to
prevent the leak of secret information. The ways on which the information flows
through the system are called channels. Channels that are not indented to transport
information are called covered channels\cite{Sabelfeld03}. These covered channels can
be classified into the following categories (in the following examples $h$ is a secret
variable and $l$ a variable that is plublic):

\begin{itemize}
\item \textit{Explicit and implicit flows}: In an explicit flow the information is leaked
      directly into some public variable (e.g. $l := h$), while in implicit flows the information
      is leaked through the control structure of the program (e.g. $\text{if}\ h = 1\ \text{then}\ l := 1\ \text{else}\ l := 0$).
\item \textit{Probabilistic channels}: If an attacker is able to run a computation multiple times
      he might be able to obtain information by looking at the probability distribution of the
      public outputs.
\item \textit{Power channels}: If the attacker has physical access to the computer or at least figure out
      the power consumption, he might be able to obtain data through the changing power consumption.
\item \textit{Resource exhausting channels}: Information also may be leaked through the exhaustion
      of finite (mostly physical) resources (e.g. a buffer overflow).
\item \textit{Termination channels}: The attacker can obtain information through the termination
      or non-termination of the computation or program.
\item \textit{Timing channels:} Information can be obtained through the time at which this action
      occurs. On the one hand \textit{external} timing channels cover the action like the termination
      of the program, where the attacker obtains information from the total execution time of the program.
      On the other hand \textit{internal} timing channels are occur in multithreaded programs through the timing difference
      between threads. For example the program \[\text{if}\ h = 1\ \{\text{sleep}(100)\}\ ;\ l := 1\ ||\ \text{sleep}(50)\ ;\ l := 0\]
      executed with most schedulers will leak the information of $h$ into $l$ through the timing difference
      if $h = 1$.
\end{itemize}
